### 2014-02-27 paper/concrete.tex
update first half of the proof.

Now, we can propose the following two-step process to ensure that
non-interference is preserved:
\Red{We should find a better name for this, or not use a name, or something.}
\begin{definition}[Non-interference preserving, restricted isomorphism (NPRI)]
  We call an IFC language
  |concreteLang alpha targetLang| (the concrete language for a given
  target language |targetLang| and scheduling policy |alpha|)
  a \textit{non-intereference preserving,
  restricted isomorphism} with regard to the IFC language
  |specLang alpha targetLang|
  (the abstract language) if the following
  two conditions hold:
  \begin{enumerate}
    \item Any of the reduction rules of the abstract
    semantics |specLang alpha targetLang|
    presented in Section~\ref{sec:retrofit} can
    be restricted by adding a predicate $P$ to the premise of
    any rule other than \textsc{I-noStep}.  The predicate $P$
    can depend only on the \textit{erased} configuration
    |erase il ic|, where |il| is the label of the first task
    in the task list and |ic| the full configuration.
    \item The concrete language
    |concreteLang alpha targetLang|
    must be isomorphic to the abstract semantics |specLang alpha targetLang|
    with the additional predicates $P$ on the rules.
  \end{enumerate}
\end{definition}

@@

\Red{Adapt the following proofs.}

\begin{lemma}
  \label{lemma:tsni}
  For any configurations |ic1|, |ic1'|, |ic2|, and label |il| where
  \begin{equation} \label{eq:tsni-lemma-lhs}
  |ic1| \approx_{|il|} |ic2|
  \qquad \text{and} \qquad
  |ic1| |.->| |ic1'|
  \end{equation}
  then there exists a configuration |ic2'| such that
  \begin{equation} \label{eq:tsni-lemma-rhs}
  |ic1'| \approx_{|il|} |ic2'|
  \qquad \text{and} \qquad
  |ic2| |.->|^* |ic2'|
  \ \text{.}
  \end{equation}
\end{lemma}

\begin{proof}
  We proof the theorem by induction on the length of the derivation sequence in~\eqref{eq:tsni-lhs}.
  The base case for derivations
  of length 0 is trivial, allowing
  us to simple chose $|ic2'=ic2|$.  In the step case, we assume
  the theorem holds for derivation sequences of length up to $n$, and show that it also
  holds for those of length $n+1$.  We split the derivation sequence from~\eqref{eq:tsni-lhs} as follows:
  \[
  |ic1| |.->| |ic1''| |.->|^n |ic1'|
  \]
  for some configuration |ic1''|.  By Lemma~\ref{lemma:tsni}, we get
  |ic''| with
  \begin{equation} \label{eq:tsni-proof-1}
  |ic1''| \approx_{|il|} |ic2''|
  \qquad \text{and} \qquad
  |ic2| |.->|^* |ic2''|
  \end{equation}
  Applying the induction hypothesis to
  $|ic1''| |.->|^n |ic1'|$, we get |ic2'| with
  \begin{equation} \label{eq:tsni-proof-2}
  |ic1'| \approx_{|il|} |ic2'|
  \qquad \text{and} \qquad
  |ic2''| |.->|^* |ic2'|
  \end{equation}
  Stitching together the derivation sequences from~\eqref{eq:tsni-proof-1} and~\eqref{eq:tsni-proof-2} directly gives
  us~\eqref{eq:tsni-rhs}, which concludes the proof.
\end{proof}
\begin{proof}[Proof of Lemma~\ref{lemma:tsni}]
  We proof the lemma by induction on the derivation
  for~\eqref{eq:tsni-lemma-lhs}, and consider all possible rules that
  could have been used to make the reduction step.
  First, we observe there must be at least one task in |ic1|, otherwise
  it could not take a step.  Thus, |ic1| is of the form
  |iconf iS1 (it1, its1)|.  Consider two cases:
  \begin{itemize}
    \item $|erase il it1|=|bullet|$. In this case, we do not need to take a
    step for
    |ic2|, because |ic2'=ic2| will already be |il|-equivalent to |ic1'|.
    To see that, note that the tasks |its1| in |ic1| are left in the
    same order and unmodified. The task |it1| either
    gets dropped (by \textsc{I-noStep}), or
    transforms into a new task |it1'| as well as potentially spawning a new
    task |it1''|.  Since both |it1'| and |it1''| have a label that is
    at least as high as the label of |it1|, they will get filtered
    by |erasef il| in |ic1'|.
    Lets consider the possible changes to |iS1|: If |it1| sends a
    message, then the corresponding queue in |iS1'| will contain one
    more message.  However, that message has the label of |it1| (or a higher
    label), and will thus get erased by |erasef il|.
    Finally, receiving or not receiving a message (by
    \textsc{I-recv} or \textsc{I-noRecv}) only changes the queue of
    task |it1|, which are erased from |iS1|.
    This ensures that $|ic1'|\approx_{|il|}|ic2'|$.

    \alphacondition{We need all scheduling policies to not change the order
      of any tasks (except for the first one).  Newly spawned task can appear
      anywhere in the list.}
    \item $|erase il it1|\neq|bullet|$.  Here, there must be a corresponding
    task |it2| in |ic2|,
    such that |it1=it2| (otherwise |ic1| and
    |ic2| could not be |il| equivalent).
    However, |it2| might not be at the beginning of the task list yet, but
    all tasks occurring before it must get erased by |erasef il|.
    In |ic2|, we can first take some number of steps until |it2| moves
    to the front of the list (\Red{Say more precisely why
      (basically because we require the scheduling policy to do that)}).

>>>>

Now, we can propose the following two-step process to ensure that
non-interference is preserved:
\Red{We should find a better name for this, or not use a name, or something.}
\begin{definition}[Non-interference preserving, restricted isomorphism (NPRI)]
  \label{def:npri}
  We call an IFC language
  |concreteLang alpha targetLang| (the concrete language for a given
  target language |targetLang| and scheduling policy |alpha|)
  a \textit{non-intereference preserving,
  restricted isomorphism} with regard to the IFC language
  |specLang alpha targetLang|
  (the abstract language) if the following
  two conditions hold:
  \begin{enumerate}
    \item Any of the reduction rules of the abstract
    semantics |specLang alpha targetLang|
    presented in Section~\ref{sec:retrofit} can
    be restricted by adding a predicate $P$ to the premise of
    any rule other than \textsc{I-noStep}.  The predicate $P$
    can depend only on the \textit{erased} configuration
    |erase il ic|, where |il| is the label of the first task
    in the task list and |ic| the full configuration.
    \item The concrete language
    |concreteLang alpha targetLang|
    must be isomorphic to the abstract semantics |specLang alpha targetLang|
    with the additional predicates $P$ on the rules.
  \end{enumerate}
\end{definition}

@@

For the proof of Theorem~\ref{thm:npri}, we first show that the
abstract language, potentially augmented with predicates as described
in the first point of Definition~\ref{def:npri}, satisfies
non-interference.  Combining this result with the isomorphism theorems
will prove the goal as desired.

\begin{theorem}
  \label{thm:rr-tsni-general}
  For any target language |targetLang|,
  the language |specLang roundrobinf targetLang| where predicates $P$
  have potentially been added to the reduction rules as described in
  Definition~\ref{def:npri} satisfies TSNI.
\end{theorem}

Theorem~\ref{thm:rr-tsni} is a simple consequence of this
(for the case where without any additional predicates).
Before we proceed with the proof of this theorem, we state a
lemma we will use.

\begin{lemma}
  \label{lemma:rr-tsni-general}
  We consider, for any target language |targetLang|,
  the information-flow control
  language |specLang roundrobinf targetLang| where a predicate $P$
  has potentially been added to the reduction rules as described in
  Definition~\ref{def:npri}.  Then,
  for any configurations |ic1|, |ic1'|, |ic2|, and label |il| where
  \begin{equation} \label{eq:tsni-lemma-lhs}
  |ic1| \approx_{|il|} |ic2|
  \qquad \text{and} \qquad
  |ic1| |.->| |ic1'|
  \end{equation}
  there exists a configuration |ic2'| such that
  \begin{equation} \label{eq:tsni-lemma-rhs}
  |ic1'| \approx_{|il|} |ic2'|
  \qquad \text{and} \qquad
  |ic2| |.->|^* |ic2'|
  \ \text{.}
  \end{equation}
\end{lemma}

\begin{proof}
  We proof the theorem by induction on the length of the derivation sequence in~\eqref{eq:tsni-lhs}.
  The base case for derivations
  of length 0 is trivial, allowing
  us to simple chose $|ic2'=ic2|$.  In the step case, we assume
  the theorem holds for derivation sequences of length up to $n$, and show that it also
  holds for those of length $n+1$.  We split the derivation sequence from~\eqref{eq:tsni-lhs} as follows:
  \[
  |ic1| |.->| |ic1''| |.->|^n |ic1'|
  \]
  for some configuration |ic1''|.  By Lemma~\ref{lemma:rr-tsni-general}, we get
  |ic''| with
  \begin{equation} \label{eq:tsni-proof-1}
  |ic1''| \approx_{|il|} |ic2''|
  \qquad \text{and} \qquad
  |ic2| |.->|^* |ic2''|
  \end{equation}
  Applying the induction hypothesis to
  $|ic1''| |.->|^n |ic1'|$, we get |ic2'| with
  \begin{equation} \label{eq:tsni-proof-2}
  |ic1'| \approx_{|il|} |ic2'|
  \qquad \text{and} \qquad
  |ic2''| |.->|^* |ic2'|
  \end{equation}
  Stitching together the derivation sequences from~\eqref{eq:tsni-proof-1} and~\eqref{eq:tsni-proof-2} directly gives
  us the right-hand side of the implication in the TSNI
  definition~\eqref{eq:tsni-rhs}, which concludes the proof.
\end{proof}
\begin{proof}[Proof of Lemma~\ref{lemma:rr-tsni-general}]
  First, we observe there must be at least one task in |ic1|, otherwise
  it could not take a step.  Thus, |ic1| is of the form
  |iconf iS1 (it1, its1)|.  Consider two cases:
  \begin{itemize}
    \item $|erase il it1|=|bullet|$.
    By the definition of |erasef il|, we know that |il canFlowTo lcurr|
    where |lcurr| is the label of |it1|.
    In this case, we do not need to take a step for
    |ic2|, because |ic2'=ic2| will already be |il|-equivalent to |ic1'|.
    To see that, note that the tasks |its1| in |ic1| are left in the
    same order and unmodified (the scheduling policy only
    modifies the first task). The task |it1| either
    gets dropped (by \textsc{I-noStep}), or
    transforms into a task |it1'| as well as potentially spawning a new
    task |it1''|.  Since both |it1'| and |it1''| have a label that is
    at least as high as the label of |it1| (can be seen
    by inspecting all reduction rules), they will get filtered
    by |erasef il| in |ic1'|.  Therefore, the |il| equivalence of the
    task list is guaranteed.
    Lets consider the possible changes to |iS1|:
    Only three reduction rules change |iS1|,
    thus it suffices to consider these cases:
    \begin{description}
      \item[Case \textsc{I-send}]
      A new message triple with label |il'| gets added to the message
      queue of the receiving thread.  However, since |lcurr canFlowTo il'|,
      the triple will get erased.
      \item[Case \textsc{I-recv} and \textsc{I-noRecv}]
      In this case, only the queue of
      task |it1| can change, which gets erased.
    \end{description}
    This ensures that $|ic1'|\approx_{|il|}|ic2'|=|ic2|$.
%    \alphacondition{We need all scheduling policies to not change the order
%      of any tasks (except for the first one).  Newly spawned task can appear
%      anywhere in the list.}
    \item $|erase il it1|\neq|bullet|$.
    Here, there must be a corresponding
    task |it2| in |ic2|,
    such that |it1=it2| (otherwise |ic1| and
    |ic2| could not be |il| equivalent).
    However, |it2| might not be at the beginning of the task list yet, but
    all tasks occurring before it must get erased by |erasef il|.
    In |ic2|, we can first take some number of steps until |it2| moves
    to the front of the list (\Red{Say more precisely why
      (basically because we require the scheduling policy to do that)}).

### 2014-02-27 paper/retrofit.tex
update first half of the proof.

\begin{theorem}[Concurrent specification language is TSNI]
For any target language |targetLang nop|, |specLang roundrobinf
(targetLang nop)| satisfies TSNI.
\end{theorem}

>>>>

\begin{theorem}[Concurrent specification language is TSNI]
  \label{thm:rr-tsni}
For any target language |targetLang nop|, |specLang roundrobinf
(targetLang nop)| satisfies TSNI.
\end{theorem}
